---
title: "GSS challange More Data"
author: "Put your name here!"
date: "put the date here"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

$H_0$ There are no significant differences in the data.  

$H_A$ There are differences in the data.

```{r eval=FALSE}
mydata <- mydata %>%
mutate(across(where(is.character), as.factor))
``` 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

We are going to use the CandP helper files to compare two categorical data types cappun and race. Because this is a cat-cat problem we will first create a bar chart, then we will run fav states to show graphical and numerical results.

$\Huge\chi^2=\sum\frac{(0-E)^2}{0}$

For inferential results we are going to run a Chi-Squared test which will tell us if there is a difference in the data but not where. Normally we will use a fisher test to do this but in this case we have more than two facotrs in "race" so will will use the fisherXY function to run fisher tests for all combinations.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")
```

The graph shows that white are favoring capitol punishment the most. Next is other and the least supportive of capitol punishment is the black.

## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```

With the white people, there are 65% of them who are in favor while 35% are opposing capitol punishment. With the group of "other" there are 55% who are in favor while 45% are opposed. With the population of black people, there are 43% who are in favor while 57% are opposed to the idea of capitol punishment.    


## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

```{r}
fisherXY (mydata$race,mydata$cappun, printAll=TRUE)
```


Based on the data above, we can say that 1300 white individuals favors capital punishment, whereas 697 were against it. Among other ethnic groups, 138 were in favor, and 112 were opposed. In the black population, 191 individuals favored capital punishment, while 257 were against it. The FisherXY test results indicate significant differences between each racial group, making all t-test results statistically significant. 

## More data version


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

With the data given to us for each branch, we were given 2,867 data points versus the 2nd branch we were given around 800 data points. This only gave us one set of data that can be seen as significant since the 2nd data set given did not have enough information to allow for there to be a significance in the Fisher XY showing the differences. We were able to see that overall for both data sets, the white population had the highest amount of those favoring the capitol punishment with other population as the second highest and the black population as the lowest.   

$H_A$ There are differences in the data.
